### 2016-08-18 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to hose stream + gas burner reports

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute
WF \> Wide Fog Stream \\
\end{tabbing}

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
ESTC \> Delaware County Emergency Services Training Center \\
NF \> Narrow Fog Stream\\
NIST \> National Institute of Standards and Technology \\
SB \> Smooth Bore Stream\\
SS \> Straight Stream \\
UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
WF \> Wide Fog Stream \\
\end{tabbing}
